---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Homework3Li

The goal of this package is to create a new class for longitudinal datasets, and implement some functions and methods for data analysis.

## Installation

You can install the released version of Homework3Li from [github](https://github.com/stephlee3/Homework3Li) with:

``` r
require(devtools)
install_github("https://github.com/stephlee3/Homework3Li")
```

## Example
We will implement some functions and methods for longitudinal data anlaysis. The function \code{make_LD} can  convert a data frame into a \code{LongitudinalData} class, and we can get the number of different subjects in the dataset when we \code{print} it.

```{r}
require(Homework3Li)
## Read in the data
library(readr)
library(dplyr)
## Load any other packages that you may need to execute your code

file_path <- system.file("extdata","MIE.csv.gz",package="Homework3Li")
dat <- read_csv(file_path,col_types = "iicdi")
x <- make_LD(dat)
print(class(x))
```

Then the function \code{subject} can filter subject-specific information, and we can get the subject ID or NULL(if the specific subject does not exist) when we \code{print} it.
```{r}
out <- subject(x, 10)
print(out)
out <- subject(x, 14)
print(out)
```

The \code{summary} function is to calculate the mean value over time at different visits and rooms for the specific subject. 
```{r}
out <- subject(x, 54) %>% summary
print(out)

out <- subject(x, 14) %>% summary
print(out)

```

Similarly, we can get functions \code{visit} and \code{room} to extract specific info from the whole dataset. The \code{print} can show the specific id, visit, or room, and \code{summary} can show the quantiles and mean value of different timepoints for a specific scenario. 
```{r}
out <- subject(x, 44) %>% visit(0) %>% room("bedroom")
print(out)

out <- subject(x, 44) %>% visit(0) %>% room("bedroom") %>% summary
print(out)

out <- subject(x, 44) %>% visit(1) %>% room("living room") %>% summary
print(out)
```
